Designing a high-performance boundary element library with OpenCL and Numba

### 2021-04-09 opencl.tex
Started performance section

\section{NUMBA ASSEMBLY OF INTEGRAL OPERATORS}

The Numba assembly of integral operators is structured differently from the OpenCL assembly. In OpenCL we create a large number of work-items that are executed in parallel on the compute device by the runtime system with the details of the parallel execution left to the device driver. For Numba we use classical loop based parallelism. Each loop iteration is the assembly of one test element with all trial elements. Within each loop we partially optimized for SIMD instruction, though this depends on the autovectorization of the just-in-time compiler and cannot be explicitly targeted in Numba. Again, we separate regular and singular interactions. In the next section we give some more details on SIMD optimization in Numba at the example of the Laplace kernel.

\section{SIMD OPTIMIZED EVALUATION OF THE LAPLACE KERNEL WITH NUMBA}

>>>>

\subsection{Avoiding data races in the global assembly}
